\bf Exploring probability distributions for bivariate temporal granularities

### 2020-02-08 main.Rmd
spell check

We will discuss the effect of the levels of cyclic granularities in this section. Recall that cyclic granularities $C_1$ and $C_2$ are such that $C_1$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_n$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_m$\}. $A_i$'s and $B_j$'s are referred to as the levels of $C_1$ and $C_2$ for all $i \in {1, 2, \dots, n}$ and $j \in {1, 2, \dots, m}$ respectively. The levels have an impact on the choice of plots since space and resolution might become a problem if the number of levels are too high. A potential approach can be to categorize the levels as very high/high/medium/low for each cyclic granularities and define some criteria based on usual cognitive power, display size available and the aesthetic mappings. Default values for these categorisations can be chosen based on levels of common temporal granularities like days-of-month, days-of-fortnight and days-of-week. For example, any levels above 31 can be considered as very high, any levels between 14 to 31 can be taken as high and that between 7 to 14 can be taken as medium and below 7 as low.

@@

These cyclic granularities are a function of the index variable and are computed based on if they are cicular (Section \ref{sec:circular-gran-def}), pseudo-circular (Section \ref{sec:quasi-circular-gran-def}) or aperiodic (Section \ref{sec:aperiodic-gran-def}). If we consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, fortnight, month, quarter, semester, year), the following cyclic time granularities can be considered for this analysis. The interval of this tsibble is 30 minutes, and hence the temporal granularities may range from half-hour to year.

@@

### Screening and visualising harmonies:

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Given the data structure <$C1$ $C2$, `general_supply_kwh`>, each of those six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to taking 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualisation. However, harmony/clash pairs can be identified among those 30 possibilties to determine feasibility of plotting any pairs together. We are left with 13 harmonies pair, each of which can be plotted together to look at the energy behavior from different perspectives.

@@

This case study shows systematic exploration of energy behavior for a random household to gain some insights on periodic behavior of the households. First, it helps us to find the list of cyclic granularities to look at, then shrinks the number of possible visualizations by identifying harmonies, visualise a harmony pair and shows the effect of different distribution plots or reverse mapping.

@@

Mumbai Indians (MI) and Chennai Super kings (CSK) are considered one of the best teams in IPL with multiple winning titles and always appearing in final playoffs from 2010 to 2015. It would be interesting to take their example in order to dive deeper into this question. Circular granularities "over-of-inning" and "inning-of-match" can be computed using \ref{sec:circular-gran-def} with over as index of the tsibble. From Figure \ref{fig:cricex}, it can be observed that there is no clear upward shift in median and quartile deviation of runs in the second innings as compared to the first innings. This might indicate that players are vulnerable to score through each over and make more runs in the first innings, whereas if they bat in the second innings they have a target in mind and are not as vulnerable. To answer Q1, winning teams like CSK and MI have indeed different startegies when it comes to batting in the first or second innings.

>>>>

We will discuss the effect of the levels of cyclic granularities in this section. Recall that cyclic granularities $C_1$ and $C_2$ are such that $C_1$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_n$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_m$\}. $A_i$'s and $B_j$'s are referred to as the levels of $C_1$ and $C_2$ for all $i \in {1, 2, \dots, n}$ and $j \in {1, 2, \dots, m}$ respectively. The levels have an impact on the choice of plots since space and resolution might become a problem if the number of levels are too high. A potential approach can be to categorize the levels as very high/high/medium/low for each cyclic granularities and define some criteria based on usual cognitive power, display size available and the aesthetic mappings. Default values for these categorizations can be chosen based on levels of common temporal granularities like days-of-month, days-of-fortnight and days-of-week. For example, any levels above 31 can be considered as very high, any levels between 14 to 31 can be taken as high and that between 7 to 14 can be taken as medium and below 7 as low.

@@

These cyclic granularities are a function of the index variable and are computed based on if they are circular (Section \ref{sec:circular-gran-def}), pseudo-circular (Section \ref{sec:quasi-circular-gran-def}) or aperiodic (Section \ref{sec:aperiodic-gran-def}). If we consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, fortnight, month, quarter, semester, year), the following cyclic time granularities can be considered for this analysis. The interval of this tsibble is 30 minutes, and hence the temporal granularities may range from half-hour to year.

@@

### Screening and visualizing harmonies:

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Given the data structure <$C1$ $C2$, `general_supply_kwh`>, each of those six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to taking 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualisation. However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting any pairs together. We are left with 13 harmonies pair, each of which can be plotted together to look at the energy behavior from different perspectives.

@@

This case study shows systematic exploration of energy behavior for a random household to gain some insights on periodic behavior of the households. First, it helps us to find the list of cyclic granularities to look at, then shrinks the number of possible visualizations by identifying harmonies, visualize a harmony pair and shows the effect of different distribution plots or reverse mapping.

@@

Mumbai Indians (MI) and Chennai Super kings (CSK) are considered one of the best teams in IPL with multiple winning titles and always appearing in final playoffs from 2010 to 2015. It would be interesting to take their example in order to dive deeper into this question. Circular granularities "over-of-inning" and "inning-of-match" can be computed using \ref{sec:circular-gran-def} with over as index of the tsibble. From Figure \ref{fig:cricex}, it can be observed that there is no clear upward shift in median and quartile deviation of runs in the second innings as compared to the first innings. This might indicate that players are vulnerable to score through each over and make more runs in the first innings, whereas if they bat in the second innings they have a target in mind and are not as vulnerable. To answer Q1, winning teams like CSK and MI have indeed different strategies when it comes to batting in the first or second innings.

### 2020-02-08 main.tex
spell check

We will discuss the effect of the levels of cyclic granularities in this section. Recall that cyclic granularities \(C_1\) and \(C_2\) are such that \(C_1\) maps index set to a set \(\{A_1, A_2, A_3, \dots, A_n\)\}, and \(C_2\) maps index set to a set \(\{B_1, B_2, B_3, \dots, B_m\)\}. \(A_i\)'s and \(B_j\)'s are referred to as the levels of \(C_1\) and \(C_2\) for all \(i \in {1, 2, \dots, n}\) and \(j \in {1, 2, \dots, m}\) respectively. The levels have an impact on the choice of plots since space and resolution might become a problem if the number of levels are too high. A potential approach can be to categorize the levels as very high/high/medium/low for each cyclic granularities and define some criteria based on usual cognitive power, display size available and the aesthetic mappings. Default values for these categorisations can be chosen based on levels of common temporal granularities like days-of-month, days-of-fortnight and days-of-week. For example, any levels above 31 can be considered as very high, any levels between 14 to 31 can be taken as high and that between 7 to 14 can be taken as medium and below 7 as low.

@@

\hypertarget{screening-and-visualising-harmonies}{%
\subsubsection{Screening and visualising harmonies:}\label{screening-and-visualising-harmonies}}

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Given the data structure \textless{}\(C1\) \(C2\), \texttt{general\_supply\_kwh}\textgreater{}, each of those six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to taking 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualisation. However, harmony/clash pairs can be identified among those 30 possibilties to determine feasibility of plotting any pairs together. We are left with 13 harmonies pair, each of which can be plotted together to look at the energy behavior from different perspectives.

@@

Mumbai Indians (MI) and Chennai Super kings (CSK) are considered one of the best teams in IPL with multiple winning titles and always appearing in final playoffs from 2010 to 2015. It would be interesting to take their example in order to dive deeper into this question. Circular granularities ``over-of-inning'' and ``inning-of-match'' can be computed using \ref{sec:circular-gran-def} with over as index of the tsibble. From Figure \ref{fig:cricex}, it can be observed that there is no clear upward shift in median and quartile deviation of runs in the second innings as compared to the first innings. This might indicate that players are vulnerable to score through each over and make more runs in the first innings, whereas if they bat in the second innings they have a target in mind and are not as vulnerable. To answer Q1, winning teams like CSK and MI have indeed different startegies when it comes to batting in the first or second innings.

>>>>

We will discuss the effect of the levels of cyclic granularities in this section. Recall that cyclic granularities \(C_1\) and \(C_2\) are such that \(C_1\) maps index set to a set \(\{A_1, A_2, A_3, \dots, A_n\)\}, and \(C_2\) maps index set to a set \(\{B_1, B_2, B_3, \dots, B_m\)\}. \(A_i\)'s and \(B_j\)'s are referred to as the levels of \(C_1\) and \(C_2\) for all \(i \in {1, 2, \dots, n}\) and \(j \in {1, 2, \dots, m}\) respectively. The levels have an impact on the choice of plots since space and resolution might become a problem if the number of levels are too high. A potential approach can be to categorize the levels as very high/high/medium/low for each cyclic granularities and define some criteria based on usual cognitive power, display size available and the aesthetic mappings. Default values for these categorizations can be chosen based on levels of common temporal granularities like days-of-month, days-of-fortnight and days-of-week. For example, any levels above 31 can be considered as very high, any levels between 14 to 31 can be taken as high and that between 7 to 14 can be taken as medium and below 7 as low.

@@

\hypertarget{screening-and-visualizing-harmonies}{%
\subsubsection{Screening and visualizing harmonies:}\label{screening-and-visualizing-harmonies}}

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Given the data structure \textless{}\(C1\) \(C2\), \texttt{general\_supply\_kwh}\textgreater{}, each of those six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to taking 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualisation. However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting any pairs together. We are left with 13 harmonies pair, each of which can be plotted together to look at the energy behavior from different perspectives.

@@

Mumbai Indians (MI) and Chennai Super kings (CSK) are considered one of the best teams in IPL with multiple winning titles and always appearing in final playoffs from 2010 to 2015. It would be interesting to take their example in order to dive deeper into this question. Circular granularities ``over-of-inning'' and ``inning-of-match'' can be computed using \ref{sec:circular-gran-def} with over as index of the tsibble. From Figure \ref{fig:cricex}, it can be observed that there is no clear upward shift in median and quartile deviation of runs in the second innings as compared to the first innings. This might indicate that players are vulnerable to score through each over and make more runs in the first innings, whereas if they bat in the second innings they have a target in mind and are not as vulnerable. To answer Q1, winning teams like CSK and MI have indeed different strategies when it comes to batting in the first or second innings.
